---
title: "hw4"
author: "Yahan Chen [chen2254@wisc.edu]"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("FITSio")
library(dplyr)
library(ggplot2)
library(readr)
library(tidyverse)
```

The challenge of HW4 is not really about the shell script command or the R code, but about understanding the fundamentals of CHTC. At the beginnign, I'm confused about 1. Where are the .tgz files 2. Where are the untared tgz files and how do I read them with my R script. The arguments and queue file from a file list are new to me that I was having a hard time understanding the functionality. Referencing the variables differently back and forth in R, shell scripts and submission file is the biggest challenge.

After I figured out this part, the codes and algorithms to find the best fits can be relatively easy.


```{r}
spectrum = read_csv("hw4best100.csv", show_col_types = FALSE) %>%
  head(10)
```

## Top 10 Matching Spectra

```{r}
cB58 = readFrameFromFITS("/home/groups/STAT_DSCP/boss/cB58_Lyman_break.fit")$FLUX
```


```{r}
n_cB58 = length(cB58)

for (idx in 1:10) {
  index = spectrum$spectrumID[idx]
  noisyi = readFrameFromFITS(paste("graph", index, sep = "/"))$flux
  n_noisyi = length(noisyi)
  
  normalized_cB58 = (cB58 - mean(cB58)) / sd(cB58)
  normalized_noisyi = (noisyi - mean(noisyi)) / sd(noisyi)

  range_cB58 = range(normalized_cB58)
  scale_factor = (range_cB58[2] - range_cB58[1]) / (max(normalized_noisyi) - min(normalized_noisyi))
  scaled_noisyi = normalized_noisyi * scale_factor

  shift = spectrum$i[idx]
  plot(x=shift+(1:n_cB58), y=normalized_cB58, type='l', col='red',
       xlab = "Shifted Wavelength", ylab = "Flux", ylim = range(range_cB58), main="Spectra Alignment")
  lines(x=1:n_noisyi, y=scaled_noisyi, type='l', col='blue')
  legend("topright", legend = c(index, "cB58"), col = c("blue", "red"), lty = 1)
}
```